Bayesian integration of networks without gold standards

### 2011-08-29 src/main/latex/paper/paper.tex
paper: small changesto results, gathering ideas for discussion

@@

The next step consists of the simulation of experimental measurements on the true graph. This is the most crucial step of the artificial testing environment as it is responsible for replicating all the different faults and problems of real data. The simplest type of error occurring in experimental measurements is random noise. This type of error is easily simulated by randomly inserting edges that do not exist in the real data and removing edges that do exist in the real data until the desired error rates are reached. The next problem is systematic error or experimental bias. This phenomenon in particular leads to the violation of stochastic independence between datasets. 
\note{TODO: Bias simulation has yet to be implemented.}%TODO <-- 
Finally, another type of error that easily escapes one's attention is the lack of negative records. Most experiments do not report which pairs of nodes do not possess an edge. As a consequence, it is hard to differentiate between node pairs that have been observed not to interact and node pairs that have not been subject to testing.

@@

\note{TODO: re-run on biased data}

@@

Figure \ref{ppi+gi} shows histograms of the existence probabilities for physical and genetic interactions from the semantically integrated dataset as calculated by the method presented here. It is apparent that \note{NUMBER}\% of the experimentally reported protein-protein interactions have been assigned probabilites less than 0.1. This is consistent with the reports of \note{PAPER}.

@@

\section{Discussion}

@@

\note{TODO: Write discussion}

>>>>

\note{TODO: Discuss value of prior odds}

@@

The next step consists of the simulation of experimental measurements on the true graph. This is the most crucial step of the artificial testing environment as it is responsible for replicating all the different faults and problems of real data. The simplest type of error occurring in experimental measurements is random noise. This type of error is easily simulated by randomly inserting edges that do not exist in the real data and removing edges that do exist in the real data until the desired error rates are reached. The next problem is systematic error, also known as experimental bias. This phenomenon in particular leads to the violation of stochastic independence between datasets. We simulate this by sampling separate false negative probabilities for each interaction and false positive probabilities for each non-interacting node-pair from Beta distributions. We then use these prepared probilities to generate false positives and false negatives in the experiments, thus introducing the same bias/systematic error. Pseudocode for this method is provided in the supplementary material.
Finally, another type of problem that easily escapes one's attention is the lack of negative records. Most experiments do not report which pairs of nodes do not possess an edge. As a consequence, it is hard to differentiate between node pairs that have been observed not to interact and node pairs that have not been subject to testing.

@@

@@

Figure \ref{ppi+gi} shows histograms of the existence probabilities for physical and genetic interactions from the semantically integrated dataset as calculated by the method presented here. A share of 39.03\% of the experimentally reported protein-protein interactions have been assigned probabilites less than 0.1. This percentage is lower than what could be expected according to the projections of Hart and colleagues \citep{hart_how_2006}.

@@

\section{Discussion}
\note{
\begin{itemize}
  \item Excellent performance despite giving competitors head start with unbiased gold standards and accurate fudge factors, which wouldn't be available normally.
  \item Other possible performance metrics (e.g. ROC curves or weighted sums)
  \item Discuss discrepancy between Hart et al and the PPI network
  \item Future work: Evaluate on simulated low-throughput
  \item Future work: Further evaluation of the algorithm using the integrated dataset
  \begin{itemize}
    \item Measure functional annotation accuracy with leave-one-out
  \end{itemize}
\end{itemize}
}

@@
